### 2024-10-24 manuscript.tex
Minor edits

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

Increasing climate model resolution is a common way of improving model accuracy
\citep{mauritsen2022}. This is of course limited by the available computational
power and a tradeoff with increasing parametrisation complexity. Current
computational availability and acceleration from general-purpose computing on
graphics processing units (GPGPUs) is progressing to enable km-scale (also
called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
general circulation models (AOGCMs) in research conditions today and
operationally in the forthcoming years. Therefore, it represents a natural
advancement in climate modeling.  Global strom-resolving models (GSRMs) are
emerging as a new front in the development of high-resolution global climate
models, with horizontal grid resolutions of about 2--8 km
\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
storms, but smaller-scale convective plumes and smaller-scale cloud structure
remain unresolved. At a 5-km scale, non-hydrostatic processes also become
important, and for this reason such models are generally non-hydrostatic. The
terms global cloud-resolving models or global convection-permitting/-resolving
models are also sometimes used interchangeably with GSRMs but imply that clouds
or convection are resolved explicitly, which is not entirely true for GSRMs, as
this would require an even higher horizontal resolution \citep{satoh2019}.
Representative of these efforts is the DYnamics of the Atmospheric general
circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
\citep{stevens2019,dyamond}, which is an intercomparison of nine global
storm-resolving models (GSRMs) on two 40-day time periods in summer (1 August
-- 10 September 2016) and winter (20 January -- 1 March 2020). A new one-year
GSRM intercomparison is currently proposed by \cite{takasuka2024}, with the
hope of also evaluating the seasonal cycle and large-scale circulation.  An
alternative to using a computationally costly GSRM is to train an artificial
neural network on GSRM output and use it for subgrid-scale clouds, as done with
the GSRM ICON by \cite{grundner2022} and \cite{grundner2023}.

@@

[TODO]

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

Increasing climate model resolution is a common way of improving model accuracy
\citep{mauritsen2022}. This is of course limited by the available computational
power and a tradeoff with increasing parametrisation complexity. Current
computational availability and acceleration from general-purpose computing on
graphics processing units (GPGPUs) is progressing to enable km-scale (also
called k-scale) Earth system models (ESMs) and coupled atmosphere--ocean
general circulation models (AOGCMs) in research conditions today and
operationally in the forthcoming years. Therefore, it represents a natural
advancement in climate modeling.  Global strom-resolving models (GSRMs) are
emerging as a new front in the development of high-resolution global climate
models, with horizontal grid resolutions of about 2--8 km
\citep{satoh2019,stevens2019}. This is enough to resolve mesoscale convective
storms, but smaller-scale convective plumes and smaller-scale cloud structure
remain unresolved. At a 5-km scale, non-hydrostatic processes also become
important, and for this reason such models are generally non-hydrostatic. The
terms global cloud-resolving models or global convection-permitting/-resolving
models are also sometimes used interchangeably with GSRMs but imply that clouds
or convection are resolved explicitly, which is not entirely true for GSRMs, as
this would require an even higher horizontal resolution \citep{satoh2019}.
Representative of these efforts is the DYnamics of the Atmospheric general
circulation Modeled On Non-hydrostatic Domains (DYAMOND) project
\citep{stevens2019,dyamond}, which is an intercomparison of nine global GSRMs
on two 40-day time periods in summer (1 August -- 10 September 2016) and winter
(20 January -- 1 March 2020). A new one-year GSRM intercomparison is currently
proposed by \cite{takasuka2024}, with the hope of also evaluating the seasonal
cycle and large-scale circulation.  An alternative to using a computationally
costly GSRM is to train an artificial neural network on GSRM output and use it
for subgrid-scale clouds, as done with the GSRM ICON by \cite{grundner2022} and
\cite{grundner2023}.

@@

The authors have made the following contributions based on the CRediT taxonomy
(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
analysis, investigation, methodology, software, writing – original draft; FB:
conceptualization, funding acquisition, project administration, supervision,
and writing – review \& editing; AM: data curation, investigation, resources,
writing – review \& editing. [TODO]
